Testing-doc-2016run

### 2024-04-29 data-prep/01-processing-schools-parcels-census.qmd
Draft up until Results done

Transfer the GeoUID from the DAs (I.e., their DA IDs) that intersect with the residential land use parcel centroids to the RED_LU sf object. (we use 'over' here instead of st_intersection because it is way faster)
```{r}
RED_LU_centroids_2011 <- sp::over(as_Spatial(st_centroid(RED_LU_2011)),as_Spatial(cen_data_2011_1 |> select(GeoUID)))
RED_LU_centroids_2011<- cbind(RED_LU_centroids_2011,st_centroid(RED_LU_2011))
```
```{r}
RED_LU_centroids_2016 <- sp::over(as_Spatial(st_centroid(RED_LU_2016)),as_Spatial(cen_data_2016_1 |> select(GeoUID)))

@@

Now transfer the TAZ ids to the RED centroids -- this is so we can pull the proportion of motor/non-motorized trips. 
```{r}
ggh_taz <- st_read("data-inputs/TTS/tts06_83_region.shp") |> st_transform(st_crs(cen_data_2011_hamiltononly))
```
Now add the TAZ IDs column to the residential parcel id
```{r}
cols_TAZIDs <-sp::over(as_Spatial(st_centroid(RED_LU_2011)),
                              as_Spatial(ggh_taz |> select(GTA06) |> rename("GTA06_Orig" = "GTA06")))
RED_LU_centroids_2011<- cbind(RED_LU_centroids_2011,cols_TAZIDs)

>>>>

Transfer the GeoUID from the DAs (I.e., their DA IDs) that intersect with the residential land use parcel centroids to the RED_LU sf object. (we use 'over' here instead of st_intersection because it is way faster)
```{r}
RED_LU_centroids_2011 <- sp::over(as_Spatial(st_centroid(RED_LU_2011)),as_Spatial(cen_data_2011_1 |> dplyr::select(GeoUID)))

RED_LU_centroids_2011_w2016ID <- sp::over(as_Spatial(st_centroid(RED_LU_2011)),as_Spatial(cen_data_2016_1 |> dplyr::select(GeoUID) |> rename("GeoUID_2016" = "GeoUID")))

RED_LU_centroids_2011 <- cbind(RED_LU_centroids_2011_w2016ID,
                              RED_LU_centroids_2011,
                              st_centroid(RED_LU_2011))
```

```{r}
RED_LU_centroids_2016 <- sp::over(as_Spatial(st_centroid(RED_LU_2016)),as_Spatial(cen_data_2016_1 |> select(GeoUID)))

@@

Now transfer the TAZ ids to the RED centroids -- this is so we can pull the proportion of motor/non-motorized trips. 
```{r}
ggh_taz <- st_read("data-inputs/TTS/tts06_83_region.shp") |> st_transform(st_crs(cen_data_2011_1))
```
Now add the TAZ IDs column to the residential parcel id
```{r}
cols_TAZIDs <-sp::over(as_Spatial(st_centroid(RED_LU_2011)),
                              as_Spatial(ggh_taz |> select(GTA06) |> rename("GTA06_Orig" = "GTA06")))
RED_LU_centroids_2011<- cbind(RED_LU_centroids_2011,cols_TAZIDs)

### 2024-04-29 data-prep/04-Creating-avail_2011-16.Rmd
Draft up until Results done

```{r}
#now let's add the communtiy names to the TAZ and summarize the % of students who use what mode by community. 
ggh_taz_communities <- st_intersection(st_centroid(ham_taz) |> st_transform(st_crs(ggh_taz)), 
                                       ham_community_bounds |> st_transform(st_crs(ggh_taz))) |>
  dplyr::select(c("GTA06", "REGION", "COMMUNITY_"))

>>>>

```{r}
#now let's add the communtiy names to the TAZ and summarize the % of students who use what mode by community. 
#NOTE: ham_taz is from 03-travel-times-TTS.qmd... add
ggh_taz_communities <- st_intersection(st_centroid(ham_taz) |> st_transform(st_crs(ggh_taz)), 
                                       ham_community_bounds |> st_transform(st_crs(ggh_taz))) |>
  dplyr::select(c("GTA06", "REGION", "COMMUNITY_"))
